Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-06-11 manuscript.Rmd
updated results

# Results
```{r}
# As shown in Table 1, `r nrow(final.list.25)` journals were included in the current study.  The mean number of years of inclusion is `r options(digits=2); mean(final.list.updated$study.time)` (median = `r options(digits=2); median(final.list.updated$study.time);`, sd =  `r options(digits=2); sd(final.list.updated$study.time)`). The overall h-Index for each journal.  The h-Index values represent the current h-Index of each journal, as opposed to the h-Index of the final study period, so these values should be interpreted cautiously.  The mean h-Index value is XXXX, (median = XXX; sd = XXX). A total of `r pretty(sum(articles.year.df$year.count))` article records were obtained across these journals.  The average number of articles per journal was `r options(digits=2); pretty(mean(articles.year.df$year.count))` (median = `r options(digits=2); pretty(median(articles.year.df$year.count))`, sd = `r options(digits=2); pretty(sd(articles.year.df$year.count))`). This figure shows consistent growth in the number of articles from 1989 to 2005.  Notable fluctuations in the number of articles was observed from 2005 to 2008, followed by growth until 2012. The decline from 2012 to 2013 should be interpreted cautiously, as this may be an artifact due to delays in indexing.  
```

### Aggregated summary (Figure 1a. 1b. -- line charts)

@@

Figure 2 is a small multiples plot, also referred to as a trellis or lattice
chart, that dis-aggregates Figures 1a and 1b.  More specifically, the small
multiples plot shows the number of articles published each year for each 
journal throughout the study time frame (orange line).  We also included data from Scopus for
comparative purposes (purple line).  The small multiples are sorted in descending
order based on the total number of article records in the HD.  The presentation
of the sort is by row, so the overall plot is read from left to right.
Abbreviations are used in Figure 2, and the full journal name is presented in
Appendix A.

>>>>

# Results

We collected a total of 3X,XXX article records from XX different databases.  Extensive cleaning procedures were applied to exclude documents that were not filtered in the original retrieval process.  More specifically, as described in the Methods section, we filtered documents to include only journals, while excluding editorials, book reviews, table of contents, and other documents that are not considered journal articles.  This reduced the total number of unique article records in the database to xx,xxxx.

## Size and growth of social work

@@

Figure 2 is a small multiples plot, also referred to as a trellis or lattice 
chart, that dis-aggregates Figures 1a and 1b.  More specifically, the small 
multiples plot shows the number of articles published each year for each journal
throughout the study time frame (orange line).  We also included data from
Scopus for comparative purposes (purple line).  The small multiples are sorted
in descending order based on the total number of article records in the HD.  The
sorting was done by row, so the overall plot so the overall plot is read from
left to right. Abbreviations are used in Figure 2, and the full journal name is
presented in Appendix A.
